---
title: "Introduction to patents"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to patents}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
The `patents` package contains a public F41 patent dataset from USPTO and 6 functions to clean and analyze the dataset. 

**Dataset**:

* `patent_data`: A dataset containing 11 columns and 51232 rows. 


**Functions**:

* `check_frequency` function checks the frequency of a column in the dataset.
* `clean_by` function cleans the dataset by a specified column.
* `freq_by_group` function checks the frequency of a column by groups.
* `separate_category` function separates the dataset into categories by columns.
* `dummy_by_condition` function creates dummy variables by a condition.
* `dummy_by_date` function creates dummy variables by date.

```{r example}
library(patents)
data('patent_data')
x1=clean_by(patent_data, "inventorState")
```
